### 2018-03-12 Writing/Thesis/content/chapter-fundamentals.tex
integrate comments part three

\begin{table}[h]
	\begin{tabularx}{\textwidth}{>{\raggedleft\arraybackslash}X | >{\raggedleft\arraybackslash}X | >{\raggedleft\arraybackslash}X | >{\raggedleft\arraybackslash}X | X}
		%\hline
		\multicolumn{1}{X}{Sepal length}	& \multicolumn{1}{X}{Sepal width}	& \multicolumn{1}{X}{Petal length}	& \multicolumn{1}{X}{Petal width} & Species			\\ \hline
				5.1			& 3.5			& 1.4			& 0.2			& Iris setosa		\\ 
				5.0			& 3.5			& 1.6			& 0.6			& Iris setosa		\\ 
				5.0			& 3.4			& 1.6			& 0.4			& Iris setosa		\\ 
				5.6			& 3.0			& 4.5			& 1.5			& Iris versicolor	\\ 				
				6.7			& 3.1			& 4.4			& 1.4			& Iris versicolor	\\ 	
				5.9			& 3.2			& 4.8			& 1.8			& Iris versicolor	\\ 	
				7.2			& 3.0			& 5.8			& 1.6			& Iris virginica		\\ 	
				5.9			& 3.0			& 5.1			& 1.8			& Iris virginica		\\ 
				6.9			& 3.1			& 5.1			& 2.3			& Iris virginica		\\ 	
	\end{tabularx}
	\caption{Features of different iris plants. This is an excerpt from the well-known iris data set \cite{iris}}
	\label{tab:iris}
\end{table}

@@

\subsection{Classification and Regression}
In addition to falling into the category of supervised learning, the problem is a classification problem. The nature of the prediction in the example is to assign one of the three classes, also called labels, 'iris setosa', iris virginica' and 'iris versicolor' to a new plant. Formally, this means that the output space $Y$ of the target function consists of a finite set of labels $\lbrace y_1,\dots,y_n\rbrace$, such that each instance of the data set is associated with a label $y_i \in Y$. In this case $Y=\lbrace '$\textit{iris setosa}$'$,$'$\textit{iris virginica}$'$, $'$\textit{iris versicolor}$' \rbrace $.

@@

\subsubsection{Ranking and Ordering}
To clarify the meaning of ranking and ordering, we return to the gardening example. After spending some time studying the different flowers, the gardener has realized they prefer certain iris species to others. He expresses his preference for a plant in a score, and labels all the plants in no particular order (see Tab. \ref{tab:ranking_vs_ordering}). An \textit{ordering} then is the result of simply ordering the labels in decreasing order of their respective score. It thus can also be given implicitly by just ordering the original classes, the flower names, as such being a permutation of the labels. A \textit{ranking}, on the other hand, assigns a fixed position to each label; for instance the rank of 'iris virginica' will always be represented by the number in the first position in the ranking, that is the number in that position denotes the \textit{rank} of the label, which is in turn defined as the label's position in the ordering. Therefore, the values in the example in Table \ref{tab:ranking_vs_ordering} result in the ranking $[2,3,1]$, whereas the ordering is $[3,1,2]$. It is notable that these can be the same, and are easily convertible. However, in the remainder of this thesis mostly the term ranking is used to identify both ranking and ordering interchangeably, especially as usually only the term 'ranking' is used.

@@

\subsection{Meta Learning}
% Context is meta learning -> what does that mean and what are the consequence
The previous discussion of machine learning problems has conceptually been about the fitting of different machine learning algorithms to problems in the form of data sets. In the context of meta learning regarding machine learning, it is researched whether it is \textquotesingle possible to learn about the learning process itself, and in particular that a system could learn to profit from previous experience to generate additional knowledge that can simplify the automatic selection of efficient models summarizing the data\textquotesingle \cite{brazdil2008metalearning}. That is, the original algorithm selection problem \cite{rice1976algorithm} is viewed as a learning problem itself that is to be tackled.

@@

To find out how well a classifier performs, it first needs to be decided which measure to consider. There are a few possibilities for this, however in this thesis the term performance measure refers to the predictive accuracy of a classifier, that is the percentage of classes that a classifier correctly identified in a given data set. But since using the whole data set to train a classifier (build a model), would skew the analysis - the classifier has already 'seen' these examples - a method for dividing data sets into train and test sets is needed.

@@

$$T_B = \frac{n_c - n_d}{\sqrt{(n_0 - n_1 )(n_0 - n_2 )}},$$
with \\
$n_c$, $n_d$, $n_0$ as above, \\
$n_1=\sum_i{t_i(t_i-1)/2}$, \\
$n_2=\sum_j{t_j(t_j-1)/2}$, \\
$t_i,$ the number of ties observed for X in the ith position of the ranking \\
$u_j,$ the number of ties observed for Y in the ith position of the ranking

Thus, the value of the tau (for both versions) lies in the interval $[-1,1]$, with 1 indicating a perfect agreement of rankings, -1 perfect disagreement, and 0 corresponding to no correlation. A high value is therefore desirable in this context, as it indicates that the prediction of the ranker agrees with the actual ranking of algorithms.

\subsection{Loss}
While the Kendall rank correlation coefficient is an indication as to what degree a predicted ranking agrees with the correct ranking of classifiers for a certain data set, it does not convey the difference in performance experienced by the user when choosing the first of the recommended algorithms compared to the performance of the actually best algorithm. This difference can be expressed in a measure called loss \cite{DBLP:conf/mldm/LeiteBV12}, which is defined as the difference of the performance of the actual best algorithm and the performance of the first recommended algorithm.

Additionally, the ranker recommends a ranking instead of a single algorithm in order to allow a user (or automated tool) to test a few of the top-ranked algorithms, which therefore also needs to be taken into account when thinking about loss. This is done here by computing a measure called best three loss, which denotes the loss resulting in the selection of the best of the first three recommended classifiers in comparison to the actual best-performing classifier in the considered set of classifiers.

>>>>

\begin{table}[h]
	\begin{tabularx}{\textwidth}{>{\raggedleft\arraybackslash}X | >{\raggedleft\arraybackslash}X | >{\raggedleft\arraybackslash}X | >{\raggedleft\arraybackslash}X | X}
		%\hline
		\multicolumn{1}{X}{Sepal length}	& \multicolumn{1}{X}{Sepal width}	& \multicolumn{1}{X}{Petal length}	& \multicolumn{1}{X}{Petal width} & Species			\\ \hline
				5.1			& 3.5			& 1.4			& 0.2			& Iris setosa		\\ 
				5.0			& 3.5			& 1.6			& 0.6			& Iris setosa		\\ 
				5.0			& 3.4			& 1.6			& 0.4			& Iris setosa		\\ 
				5.6			& 3.0			& 4.5			& 1.5			& Iris versicolor	\\ 				
				6.7			& 3.1			& 4.4			& 1.4			& Iris versicolor	\\ 	
				5.9			& 3.2			& 4.8			& 1.8			& Iris versicolor	\\ 	
				7.2			& 3.0			& 5.8			& 1.6			& Iris virginica		\\ 	
				5.9			& 3.0			& 5.1			& 1.8			& Iris virginica		\\ 
				6.9			& 3.1			& 5.1			& 2.3			& Iris virginica		\\ 	
	\end{tabularx}
	\caption{Features of different iris plants. This is an excerpt from the well-known iris data set \cite{iris}.}
	\label{tab:iris}
\end{table}

@@

\subsection{Classification and Regression}
In addition to falling into the category of supervised learning, the problem is a classification problem. The nature of the prediction in the example is to assign one of the three classes, also called labels, `iris setosa', `iris virginica' and `iris versicolor' to a new plant. Formally, this means that the output space $Y$ of the target function consists of a finite set of labels $\lbrace y_1,\dots,y_n\rbrace$, such that each instance of the data set is associated with a label $y_i \in Y$. In this case, the output space is defined as $Y=\lbrace '$\textit{iris setosa}$'$,$'$\textit{iris virginica}$'$, $'$\textit{iris versicolor}$' \rbrace $.

@@

\subsubsection{Ranking and Ordering}
To clarify the meaning of ranking and ordering, we return to the gardening example. After spending some time studying the different flowers, the gardener has realized they prefer certain iris species to others. They express their preference for a plant in a score, and labels all the plants in no particular order (see Tab. \ref{tab:ranking_vs_ordering}). An \textit{ordering} then is the result of simply ordering the labels in decreasing order of their respective score. It thus can also be given implicitly by just ordering the original classes, the flower names, as such being a permutation of the labels. A \textit{ranking}, on the other hand, assigns a fixed position to each label; for instance the rank of `iris virginica' will always be represented by the number in the first position in the ranking, that is the number in that position denotes the \textit{rank} of the label, which is in turn defined as the label's position in the ordering. Therefore, the values in the example in Table \ref{tab:ranking_vs_ordering} result in the ranking $[2,3,1]$, whereas the ordering is $[3,1,2]$. It is notable that these can be the same, and are easily convertible. However, in the remainder of this thesis mostly the term ranking is used to identify both ranking and ordering interchangeably, especially as usually only the term `ranking' is used.

@@

\subsection{Meta Learning}
% Context is meta learning -> what does that mean and what are the consequence
The previous discussion of machine learning problems has conceptually been about the fitting of different machine learning algorithms to problems in the form of data sets. In the context of meta learning regarding machine learning, it is researched whether it is `possible to learn about the learning process itself, and in particular that a system could learn to profit from previous experience to generate additional knowledge that can simplify the automatic selection of efficient models summarizing the data' \cite{brazdil2008metalearning}. That is, the original algorithm selection problem \cite{rice1976algorithm} is viewed as a learning problem itself that is to be tackled.

@@

To find out how well a classifier performs, it first needs to be decided which measure to consider. There are a few possibilities for this, however in this thesis the term performance measure refers to the predictive accuracy of a classifier, that is the percentage of classes that a classifier correctly identified in a given data set. But since using the whole data set to train a classifier (build a model), would skew the analysis - the classifier has already `seen' these examples - a method for dividing data sets into train and test sets is needed.

@@

$$T_B = \frac{n_c - n_d}{\sqrt{(n_0 - n_1 )(n_0 - n_2 )}},$$
with \\
$n_c$, $n_d$, $n_0$ as above, \\
$n_1=\sum_i{t_i(t_i-1)/2}$, \\
$n_2=\sum_j{u_j(u_j-1)/2}$, \\
$t_i,$ the number of ties observed for X in the ith position of the ranking \\
$u_j,$ the number of ties observed for Y in the jth position of the ranking

Thus, the value of the tau (for both versions) lies in the interval $[-1,1]$, with 1 indicating a perfect agreement of rankings, -1 for a perfect disagreement, and 0 corresponding to no correlation. A high value is therefore desirable in this context, as it indicates that the prediction of the ranker agrees with the actual ranking of algorithms.

\subsection{Loss}
While the Kendall rank correlation coefficient is an indication as to what degree a predicted ranking agrees with the correct ranking of classifiers for a certain data set, it does not convey the difference in performance experienced by the user when choosing the first of the recommended algorithms compared to the performance of the actually best algorithm. This difference can be expressed in a measure called loss \cite{DBLP:conf/mldm/LeiteBV12}, which is defined as the difference of the performance of the actual best algorithm and the performance of the first recommended algorithm. Therefore, the loss in performance $L$ a user experiences on a data set when following a ranker's recommendation by choosing the first algorithm in the returned ranking can be expressed as

$$L=|p_{\textit{best}}-p_{\textit{first}}|$$
with \\
$p_{\textit{best}}$, the performance of the best algorithm on the data set, \\
$p_{\textit{first}}$, the  performance of the first recommended algorithm on the data set.

Taking the absolute value of the difference is necessary here, since the `best' performance value of a classifier does not always need to be the largest value. When choosing the error rate of a classifier on a data set as the performance value, for example, the best possible value is 0, and in general, all classifiers besides the best one will have an equal or higher performance value. When choosing the percentage of correctly classified instances, though, the opposite is true, but the loss always needs to be non-negative. This is ensured by the taking the absolute value of the difference.

However, the ranker recommends a \textit{ranking} instead of a single algorithm in order to allow a user (or automated tool) to test a few of the top-ranked algorithms, which therefore also needs to be taken into account when thinking about loss. This is done here by computing a measure called best three loss (B3L), which denotes the loss resulting in the selection of the best of the first three recommended classifiers in comparison to the actual best-performing classifier in the considered set of classifiers. Similar to the definition above, the loss in performance a user experiences on a data set when following a ranker's recommendation by choosing the best of the first three recommended algorithms can be expressed as

$$\textit{B3L}=|p_{\textit{best}}-\textit{max}(p_{\textit{first}}, p_{\textit{second}}, p_{\textit{third}})|$$
with \\
$p_{\textit{best}}$, $p_{\textit{first}}$ as above, \\
$p_{\textit{second}}$, the performance of the second recommended algorithm on the data set. \\
$p_{\textit{third}}$, the performance of the third recommended algorithm on the data set.

It is notable that this definition is only valid if the `best' performance value is the largest possible value, as for example is the case for the percentage of correctly classified instances, as explained above. When choosing a measure like the error rate, where the lowest value is the best value, the maximum in the equation needs to be substituted by a minimum, since the best of the first three recommended algorithms then is the one with the \textit{lowest} performance value.

To demonstrate how the loss measures work, we return to the gardener example from the previous sections. Previously, the gardener has just chosen a tree-based model (see Fig. \ref{fig:decision_tree}) and hoped that this was a good approximation. But they conclude that the error rate of this model is too high, and a better approximation is needed. So instead, they now choose to use an AutoML tool that will return a ranking of classification algorithms for their data set of flowers, a ranker. The ranker has four available algorithms $A_1$, $A_2$, $A_3$ and $A_4$, and has produced the ranking depicted in Tab. \ref{tab:lossTable}. When the gardener follows this recommendation, the loss $L$ experienced is $L=|0.1-0.3|=0.2$, and $\textit{B3L}=|0.1-\textit{min}(0.3,0.1,0.4)|=0$. So by trying the best three recommended algorithms, the gardener finds the best of the four available algorithms. But the example also shows, that the loss is always viewed only regarding the algorithms that are contained in the ranking, not all available algorithms - the algorithms $A_1$ to $A_4$ are only compared among each other and not, for example, with the tree model constructed earlier.

\begin{table}
\begin{tabularx}{\textwidth}{X | X | X | X | X}
			& $A_1$	& $A_2$	& $A_3$	& $A_4$ \\\hline
error rate	& 0.1	& 0.7	& 0.3	& 0.4	\\
rank			& 2		& 4		& 1		& 3	
\end{tabularx}
\caption{An exam.}
\label{tab:lossTable}
\end{table}

### 2018-03-12 Writing/Thesis/content/chapter-related-work.tex
integrate comments part three

% Active testing A3R
The second approach does not initially use meta knowledge and is called active testing. Active testing is a strategy that \textquotesingle intelligently selects the most useful tests\textquotesingle \cite{DBLP:journals/ml/AbdulrahmanBRV18} to perform on a given data sets. Tests in this context mean the evaluation of a classifier that is considered for the ranking on the given data set. The authors improved this strategy by reducing the time needed to identify a good algorithm by, similarly to the rank aggregation variant, incorporating time in the estimations made by the strategy which previously only compared accuracy values.

\section{Algorithm and Hyperparameter Selection}
\label{sec:related:cash}
%% CASH
Taking it a step further than predicting rankings of classification algorithms with fixed hyperparameters is additionally optimizing the classifier's hyperparameters, which has been defined as \textquotesingle the combined algorithm selection and hyperparameter optimization problem (short: CASH)\textquotesingle \cite{thornton2013auto}. Two widely used approaches of this kind are Auto-WEKA and AUTO-SKLEARN. It has to be noted that thus these approaches also go further than the solution proposed in this thesis, which currently only takes into account one fixed hyperparameter configuration for each classification algorithm.

% Auto-WEKA
Auto-WEKA is an AutoML tool that both selects a machine learning algorithm and optimizes its hyperparameters by using Bayesian optimization \cite{thornton2013auto}. It was first released in 2013 as an extension to the popular data mining software WEKA \cite{hall2009weka}, which also offers a user-friendly GUI in addition to a command-line interface and an API, to assist the large number of novice users of the software in selecting parametrized algorithms for their problems. The tool has since grown in popularity and is in version 2.0 as of March 2016 \cite{kotthoff2016auto}. In Auto-WEKA, the problem of selecting an algorithm and its hyperparameters is combined by treating the algorithm itself as a hyperparameter and searching the joint space of algorithms and hyperparameters for the best solution. An input data set is first preprocessed by means of feature selection. Then, Sequential Model-Based Optimization for General Algorithm Configuration (SMAC) is used to \textquotesingle iterate [...] between fitting models and using them to make choices about which configurations to investigate\textquotesingle  \cite{hutter2011sequential}. In the case of Auto-WEKA, this means that during the optimization process, a model is built, a configuration of hyperparameters that is promising regarding the current model and training data is tried out, and the result is fed back to the model. This cycle is then repeated until the allocated time has run out. Auto-WEKA exploits hard-coded meta-knowledge, that is considering past performances of algorithms, to make decisions by always trying algorithms like Random Forest, which perform well on a large number of data sets, first. \\

@@

\section{Constructing pipelines}
\label{sec:related:pipelines}
%% Whole pipelines
Before a classifier is evaluated on a data set, often a number of pre-processing steps are executed first. This includes, for example, selecting promising features and discarding others, and normalizing the data. The \textquotesingle sequence of tasks that need to be performed to classify instances belonging to a given dataset into a set of predefined categories\textquotesingle \cite{DBLP:conf/eurogp/SaPOP17} can therefore be defined as a classification pipeline. Two tools which construct such complete pipelines for data sets are ML-Plan and the RECIPE framework.

% ML-Plan
ML-Plan is an AutoML tool that instead of concentrating on hyperparameter optimization, aims to optimize the whole machine-learning pipeline \cite{wever2017automatic}. This is achieved by viewing machine-learning as a task, building a hierarchical task network out of the resulting subtasks, and then searching for a solution in the induced tree structure. In the tree, the root node contains the complex task of building a machine learning pipeline, inner nodes represent incomplete pipelines consisting of complex and possibly also primitive tasks, and leaf nodes are complete pipelines that include only primitive tasks. An example of this might be 'classify' as the root node, with an intermediate node on some level that contains the tasks 'build NN', 'train NN' and 'predict from NN'. The complex task 'build NN' would then further be decomposed, and could lead to a leaf node with n tasks 'Add layer', 'train NN' and 'predict from NN', which are all primitive tasks that do not need to be further decomposed. A best-first search algorithm in a modified variant is then used to find good solutions in this task network. For the actual implementation of the learning algorithms, WEKA is used. Like Auto-WEKA, ML-Plan uses hard-coded meta-knowledge by using a fixed orders as to which classifiers are tried first. However, the authors find that their results exceed those achieved by Auto-WEKA.\\

\begin{figure}
\centering
\includegraphics[width=.8\textwidth]{gfx/MLPlan.pdf}
\caption{An example for how the complex task \textquotesingle classify\textquotesingle might be broken down by ML-Plan, adapted from \cite{wever2017automatic}. Nodes containing \textquotesingle ...\textquotesingle represent an undefined number of subtrees.}
\label{fig:mltree}
\end{figure}

% Recipe framework
Similar to ML-PLAN, the RECIPE framework constructs whole classification pipelines for new problems \cite{DBLP:conf/eurogp/SaPOP17}. However, this is done by means of grammar-based genetic programming: the tasks that the pipeline is composed of are represented by a grammar, which 'is used to generate the initial population, as well as to constrain the crossover and mutation operations, which always need to be valid according to the grammar' \cite{DBLP:conf/eurogp/SaPOP17}. This means that generated individuals representing complete pipelines can never be invalid. So for a new data set combined with a grammar that represents the valid pipelines, the tool first initializes the first generation according to the grammar. The fitness of individuals is then evaluated by mapping them to their respective implementations in the scikit-learn framework, and a new generation is created that takes this newly gained information into account. Evaluation by the authors indicates that the RECIPE framework is able to compete with AUTO-SKLEARN and a different evolutionary approach, although it does not incorporate meta-knowledge in the search. It is notable that another evolutionary approach, Tree-based Pipeline Optimization Tool (TPOT) \cite{olson2016automating} exists, although in comparison to the RECIPE framework, it can generate individuals that represent invalid pipelines.

>>>>

% Active testing A3R
The second approach does not initially use meta knowledge and is called active testing. Active testing is a strategy that `intelligently selects the most useful tests' \cite{DBLP:journals/ml/AbdulrahmanBRV18} to perform on a given data sets. Tests in this context mean the evaluation of a classifier that is considered for the ranking on the given data set. The authors improved this strategy by reducing the time needed to identify a good algorithm by, similarly to the rank aggregation variant, incorporating time in the estimations made by the strategy which previously only compared accuracy values.

\section{Algorithm and Hyperparameter Selection}
\label{sec:related:cash}
%% CASH
Taking it a step further than predicting rankings of classification algorithms with fixed hyperparameters is additionally optimizing the classifier's hyperparameters, which has been defined as `the combined algorithm selection and hyperparameter optimization problem (short: CASH)' \cite{thornton2013auto}. Two widely used approaches of this kind are Auto-WEKA and AUTO-SKLEARN. It has to be noted that these approaches also go further than the solution proposed in this thesis, which currently only takes into account one fixed hyperparameter configuration for each classification algorithm.

% Auto-WEKA
Auto-WEKA is an AutoML tool that both selects a machine learning algorithm and optimizes its hyperparameters by using Bayesian optimization \cite{thornton2013auto}. It was first released in 2013 as an extension to the popular data mining software WEKA \cite{hall2009weka}, which also offers a user-friendly GUI in addition to a command-line interface and an API, to assist the large number of novice users of the software in selecting parametrized algorithms for their problems. The tool has since grown in popularity and is in version 2.0 as of March 2016 \cite{kotthoff2016auto}. In Auto-WEKA, the problem of selecting an algorithm and its hyperparameters is combined by treating the algorithm itself as a hyperparameter and searching the joint space of algorithms and hyperparameters for the best solution. An input data set is first preprocessed by means of feature selection. Then, Sequential Model-Based Optimization for General Algorithm Configuration (SMAC) is used to `iterate [...] between fitting models and using them to make choices about which configurations to investigate' \cite{hutter2011sequential}. In the case of Auto-WEKA, this means that during the optimization process, a model is built, a configuration of hyperparameters that is promising regarding the current model and training data is tried out, and the result is fed back to the model. This cycle is then repeated until the allocated time has run out. Auto-WEKA exploits hard-coded meta-knowledge, that is considering past performances of algorithms, to make decisions by always trying algorithms like Random Forest, which perform well on a large number of data sets, first. \\

@@

\section{Constructing pipelines}
\label{sec:related:pipelines}
%% Whole pipelines
Before a classifier is evaluated on a data set, often a number of pre-processing steps are executed first. This includes, for example, selecting promising features and discarding others, and normalizing the data. The `sequence of tasks that need to be performed to classify instances belonging to a given dataset into a set of predefined categories' \cite{DBLP:conf/eurogp/SaPOP17} can therefore be defined as a classification pipeline. Two tools which construct such complete pipelines for data sets are ML-Plan and the RECIPE framework.

% ML-Plan
ML-Plan is an AutoML tool that instead of concentrating on hyperparameter optimization, aims to optimize the whole machine-learning pipeline \cite{wever2017automatic}. This is achieved by viewing machine-learning as a task, building a hierarchical task network out of the resulting subtasks, and then searching for a solution in the induced tree structure. In the tree, the root node contains the complex task of building a machine learning pipeline, inner nodes represent incomplete pipelines consisting of complex and possibly also primitive tasks, and leaf nodes are complete pipelines that include only primitive tasks. An example of this might be `classify' as the root node, with an intermediate node on some level that contains the tasks `build NN', `train NN' and `predict from NN'. The complex task `build NN' would then further be decomposed, and could lead to a leaf node with n tasks `Add layer', `train NN' and `predict from NN', which are all primitive tasks that do not need to be further decomposed. A best-first search algorithm in a modified variant is then used to find good solutions in this task network. For the actual implementation of the learning algorithms, WEKA is used. Like Auto-WEKA, ML-Plan uses hard-coded meta-knowledge by using a fixed orders as to which classifiers are tried first. However, the authors find that their results exceed those achieved by Auto-WEKA.\\

\begin{figure}
\centering
\includegraphics[width=.8\textwidth]{gfx/MLPlan.pdf}
\caption{An example for how the complex task `classify' might be broken down by ML-Plan, adapted from \cite{wever2017automatic}. Nodes containing `...' represent an undefined number of subtrees.}
\label{fig:mltree}
\end{figure}

% Recipe framework
Similar to ML-PLAN, the RECIPE framework constructs whole classification pipelines for new problems \cite{DBLP:conf/eurogp/SaPOP17}. However, this is done by means of grammar-based genetic programming: the tasks that the pipeline is composed of are represented by a grammar, which `is used to generate the initial population, as well as to constrain the crossover and mutation operations, which always need to be valid according to the grammar' \cite{DBLP:conf/eurogp/SaPOP17}. This means that generated individuals representing complete pipelines can never be invalid. So for a new data set combined with a grammar that represents the valid pipelines, the tool first initializes the first generation according to the grammar. The fitness of individuals is then evaluated by mapping them to their respective implementations in the scikit-learn framework, and a new generation is created that takes this newly gained information into account. Evaluation by the authors indicates that the RECIPE framework is able to compete with AUTO-SKLEARN and a different evolutionary approach, although it does not incorporate meta-knowledge in the search. It is notable that another evolutionary approach, Tree-based Pipeline Optimization Tool (TPOT) \cite{olson2016automating} exists, although in comparison to the RECIPE framework, it can generate individuals that represent invalid pipelines.
